\texttt{GLAD-M25} - global adjoint tomography model

### 2018-09-25 gji_extraguide.tex
Updates from ShareLaTeX

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
\end{figure}

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
\end{figure}

@@

@@

\begin{thebibliography}{}  
  \bibitem[Butcher(1992)]{bu}  
    Butcher J. 1992. {\it Copy-editing: The Cambridge  
    Handbook}, 3rd edn, Cambridge Univ. Press, Cambridge.
  \bibitem[The Chicago Manual(1982)]{cm}  
    {\it The Chicago Manual of Style}, Univ.   
    Chicago Press, Chicago, 1982.
  \bibitem[Chao(1985)]{ch} 
    Chao, B. F., 1985. Normal mode study of the Earth's rigid 
     body motions, {\it Geophys. Res. Lett.}, {\bf 12}, 526-529.
  \bibitem[Hinderer(1986)]{hi}  
    Hinderer, J., 1986. Resonance effects of the earth's fluid
    core in earth rotation, in {\it Solved and Unsolved 
    Problems}, pp. 277-296, ed. Cazenave A., Reidel, 
    Dordrecht.
  \bibitem[Kopka \& Daly(1995)]{kd}  
    Kopka H. \& Daly P.W., 1995, \textit{A guide to} \LaTeX2e,
    Addison--Wesley, New York  
  \bibitem[Lamport(1986)]{la}  
    Lamport L., 1986,  \LaTeX: {\it A Document   
    Preparation System}, Addison--Wesley, New York  
  \bibitem[Lindberg (1986)]{bl}  
    Lindberg, C., 1986.  Multiple taper harmonic analysis of 
    terrestrial free oscillations, {\it PhD thesis}, 
    University of California.
  \bibitem[Maupin(1992)]{ma} 
    Maupin, V., 1992. Modelling of laterally trapped surface 
    waves with application to Rayleigh waves in the Hawaiian 
    swell, {\it Geophys. J. Int.}. {\bf 110}, 553-570.     	
  \bibitem[Rutherford \& Hawker(1981)]{rh}
      Rutherford, S. R. \& Hawker, K. E., 1981, 
    Consistent coupled mode theory of sound propagation for a 
    class of non-separable problems, 
   {\it J. acoust. Soc. Am.}, {\bf 71}, 554-564
\end{thebibliography}

>>>>

%\begin{figure}[h]
%    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
%\end{figure}

%\begin{figure}[h]
%    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Macdonald_Yellowstone.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Pitcairn_Guadalupe.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_Hawaii.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Samoa_MarquesasS1.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=1.0\textwidth]{figures/plumes/Tahiti_Macdonald.png}\label{fig:f}}\\
%    \caption{Vertical cross sections of shear wave velocity perturbations of plumes in the pacific region.}
%\end{figure}

@@

\cite{zhu2012structure}

@@

\bibliographystyle{gji}
\bibliography{ref.bib}
